### 2016-07-04 text/formal_background.tex
Add more on homomorphisms.

\subsection{Homomorphisms}
\label{subsec:typed_graphs}

@@

However, our technique of symbolic execution of transformation rules means that we cannot rely on a trivial homomorphism. Instead we must... \bentley{TODO: Finish this sentence.}

Matching:

\begin{itemize}

\item Rules onto rules?
\begin{itemize}
\item If so, is isomorphic
\end{itemize}

\item Contracts onto path conditions
\begin{itemize}
\item Edges: Each edge of contract must exist injectively in PC
\item Vertices: Each vertex match must be surjective from target to source. Note that this will be a partial function. This should also be a minimal function.
\end{itemize}

\item Rules onto path conditions

\item Path conditions onto transformation executions

\item Do we want to add slicing?
\end{itemize}

@@

The first typed graph homomorphism we define is the trivial one. This is presented in order to

@@

Our technique also requires a form of graph homomorphism that primarily focuses on matching the edges of the graphs. This homomorphism will be an injective match regarding the edges, but note that a particular vertex in the source graph may match onto multiple vertices in the target graph. \bentley{What's the term for this?}

@@

A typed graph edge homomorphism between $g$ and $g'$ is a function $h: h_v \cup h_e$ such that:
\begin{itemize}
\item $h_v: V'\rightarrow V$
\begin{itemize}
\item Note that $h_v$ is an function from a vertex in the target graph onto a vertex in the source graph
\end{itemize}
\item $h_e: E\rightarrow E'$
\item $\forall v_1 \xrightarrow{e} v_2\in E$:
\begin{itemize}
\item Let $e' = h_e(e), v_1' = s'(e'), v_2' = t'(e')$
\item $v_1', v_2' \in V', e' \in E'$
\item $v_1 = h_v(v_1'), v_2 = h_v(v_2')$
\item $\mathit{matchesOver}(\tau(v_1), \tau(v_1') \land \\\mathit{matchesOver}(\tau(v_2), \tau(v_2') \land\\ \mathit{matchesOver}(\tau(e), \tau(e')$
\end{itemize}

>>>>

\subsection{Homomorphisms}
\label{subsec:homomorphisms}

@@

However, our technique of symbolic execution of transformation rules means that we cannot rely on a trivial homomorphism. Instead our matching must be flexible about how vertices in the source graph may match over multiple vertices in the target graph.

@@

The first typed graph homomorphism we define is standard, where the structure of the source graph must be found in the target graph. This is presented for the reader to appreciate the complications required for the next homomorphisms.

@@

Our technique also requires a form of graph homomorphism that primarily focuses on matching the edges of the graphs. This homomorphism will be an injective\footnote{For a terminology refresh, \textit{injective matching} means there is a one-to-one correspondence between the source and target vertices. \textit{Surjective matching} means that all target vertices must be matched by at least one source vertex. }match regarding the edges, but note that a particular vertex in the source graph may match onto multiple vertices in the target graph. \bentley{What's the term for this?}

@@

A typed graph edge homomorphism between $g$ and $g'$ is a function $h: h_v \cup h_e$ such that:
\begin{itemize}
\item $h_v: V'\rightarrow V$ Note that this function has unusual properties:
\begin{itemize}

\item A function from a vertex in the target graph onto a vertex in the source graph
\item A partial function, as not all vertices in the target graph will be reflected in the source graph
\item Surjective, so that all source vertices are matched to target vertices
\item A minimal function, such that the minimum number of target  vertices are matched to each source vertex \bentley{Not sure if this is needed.}
\end{itemize}
\item $h_e: E\rightarrow E'$, and is injective
\item $\forall v_1 \xrightarrow{e} v_2\in E$:
\begin{itemize}
\item Let $e' = h_e(e), v_1' = s'(e'), v_2' = t'(e')$
\item $v_1', v_2' \in V', e' \in E'$
\item $v_1 = h_v(v_1'), v_2 = h_v(v_2')$
\item $\mathit{matchesOver}(\tau(v_1), \tau(v_1') \land \\\mathit{matchesOver}(\tau(v_2), \tau(v_2') \land\\ \mathit{matchesOver}(\tau(e), \tau(e')$
\end{itemize}
